Inputing Weights

### 2023-05-12 src/03_input_weights.Rmd
added psuedocode

```{r echo=FALSE}

unfiltered_msas <- 
real_estate_metrics <- read_xlsx(here("data/intermediate/metric_data.xlsx"), sheet="real_estate_metrics") %>% 
  select(cbsa, anchor_city, msa, starts_with("n_")) %>% 
  mutate(cbsa = factor(cbsa))

landlord_metrics <- read_xlsx(here("data/intermediate/metric_data.xlsx"), sheet="landlord_metrics") %>% 
  select(cbsa, starts_with("n_"))%>% 
  mutate(cbsa = factor(cbsa))

@@

reopt_metrics <- read_xlsx(here("data/intermediate/metric_data.xlsx"), sheet="reopt_metrics") %>% 
  select(cbsa, starts_with("n_")) %>% 
  mutate(cbsa = factor(cbsa))

@@

client_weights <- c(0.18, 0.07, 0.11, 0.07, 0.0, 0.07, 0.50)

@@

client_test <- calculate_wt_criteria(unwt_criteria, client_weights)
```

@@

## Inputs and Outputs

## Embedded Application

```{r tabsets, echo=FALSE}
shinyAppFile(
  here("solar_fam_shiny/app.R"),
  options = list(
    width = "100%", height = 550
  )
)
```

>>>>

```{r echo=FALSE}
# list of MSAs without filtering population size
unfiltered_msas <- read_csv(here("data/intermediate/unfilter_msas.csv"))
real_estate_metrics <- read_csv(here("data/intermediate/demographic_data.csv")) %>% 
  select(cbsa, anchor_city, msa, starts_with("n_")) %>% 
  mutate(cbsa = factor(cbsa))

landlord_metrics <- read_csv(here("data/intermediate/landlord_data.csv")) %>% 
  select(cbsa, starts_with("n_"))%>% 
  mutate(cbsa = factor(cbsa))

@@

reopt_metrics <- read_csv(here("data/intermediate/reopt_metrics")) %>% 
  select(cbsa, starts_with("n_")) %>% 
  mutate(cbsa = factor(cbsa))

@@

@@

@@
